Quantifying the Impact \\ of Performance Improvements and Cost Reductions \\ from 20 years of Light-Emitting Diode Manufacturing

### 2021-02-05 SPIE/article/main.tex
corrected citations, added equation to methods section

For instance, a highly cited and frequently updated metric is the total flux per package \cite{Liu2009}\cite{haitz2011solid}\cite{cho2017white}\cite{Fontoynont2018}. In combination with the cost per total flux, this visualization is sometimes referred to as \textit{"Haitz's Law"}, in reference to an early report on LED development by Haitz et al. \cite{haitz1999case}. However, while these metrics are often used to showcase technological progress in light-emitting diode design and manufacturing, they have limited significance XXX. Firstly, it is not desirable in all applications to increase the total flux per device beyond a certain point. Reasons for limiting the total flux per device may include lighting design considerations to reduce glare \cite{khan2015led}, device efficiency considerations to avoid electrical droop at high operating currents associated with high brightness \cite{Piprek2010} and economical considerations where multiple LED die in a single package can achieve the same brightness as a single high-brightness LED die. Secondly, even if one were to disregard these limitations, the total flux per device would only be a proxy for technological improvements in light-emitting diodes, if it was referring to single chips, instead of multi-chip paackages. 
Figure \ref{fig:haitz} shows an updated and expanded overview of best performing devices, both at the chip and package level, inspired by \textit{"Haitz's Law"}. It is evident that the historical improvement in total flux per package for single chips is not as pronounced as for multi-chip packages. While \textit{"Haitz's Law"} remains a popular visualization related to the progress in light-emitting diode design and manufacturing, care must be taken to consider its limitations.

@@

Flicker \cite{weinold2020long}

@@

\begin{figure} [ht]
    \begin{center}
        \includegraphics[width=\textwidth]{SPIE/article/cct_spectrum.pdf}
    \end{center}
    \caption{Color temperature for temperature values between 1,000K and 12,000K. Vertical lines indicate the color temperature of blue light emitting diodes used in combinations with phosphors. Two data points are shown: The 1997 \textit{Nichia} \ch{YAG:Ce^{3+}} (YAG) phosphor at 5800K and the 2004 \textit{Lumileds} \ch{Sr_2Si_5N_8:Eu^{2+}} ("258") phosphor at below 4000K. Color data generated using the \textit{luxpy} package for \textit{Python}. CCT for phosphors computed using the \textit{color science} package for \textit{Python}, from spectral data in Bando et al.  \cite{bando1998development} and Mueller-Mach et al.\cite{MuellerMach2005}.}
    \label{fig:cct}
\end{figure}

\clearpage

\section{METHODS}
\label{sec:methods}

@@

@@

\begin{figure} [ht]
    \begin{center}
        \includegraphics[width=\textwidth]{SPIE/article/chip_architectures.pdf}
    \end{center}
    \caption{Cutaway side views of the evolution of chip architectures for classical chip designs (lateral current spreading). Note that dimensions are not to scale and smaller features are greatly exaggerated for visibility. Years correspond to earliest identified patent priority date. Dashed boxes indicate chip designs not brought to large scale production. Adapted from patents \cite{nagahama2013nitride}\cite{tanaka2010semiconductor}\cite{wierer2006photonic}}
    \label{fig:chip_arch}
\end{figure}

\begin{figure} [ht]
    \begin{center}
        \includegraphics[width=0.85\textwidth]{SPIE/article/droop_lumileds.pdf}
    \end{center}
    \caption{Luminous intensity of four different \textit{Lumileds} high-power light-emitting diodes normalized to the value at a test current of $A_{test}=350$mA. The black curves describe the real measured intensity, the orange curves describe the estimated ideal intensity. Droop is the difference between these curves at the test current. Current-Intensity data extracted from device datasheets \cite{datasheet_lumileds_lux1}\cite{datasheet_lumileds_rebel}\cite{datasheet_lumileds_rebplus}\cite{lumi2019data}}
    \label{fig:chip_arch}
\end{figure}

>>>>

For instance, a highly cited and frequently updated metric is the total flux per package \cite{Liu2009,haitz2011solid,cho2017white,Fontoynont2018}. In combination with the cost per total flux, this visualization is sometimes referred to as \textit{"Haitz's Law"}, in reference to an early report on LED development by Haitz et al. \cite{haitz1999case}. However, while these metrics are often used to showcase technological progress in light-emitting diode design and manufacturing, they have limited significance XXX. Firstly, it is not desirable in all applications to increase the total flux per device beyond a certain point. Reasons for limiting the total flux per device may include lighting design considerations to reduce glare \cite{khan2015led}, device efficiency considerations to avoid electrical droop at high operating currents associated with high brightness \cite{Piprek2010} and economical considerations where multiple LED die in a single package can achieve the same brightness as a single high-brightness LED die. Secondly, even if one were to disregard these limitations, the total flux per device would only be a proxy for technological improvements in light-emitting diodes, if it was referring to single chips, instead of multi-chip paackages. 
Figure \ref{fig:haitz} shows an updated and expanded overview of best performing devices, both at the chip and package level, inspired by \textit{"Haitz's Law"}. It is evident that the historical improvement in total flux per package for single chips is not as pronounced as for multi-chip packages. While \textit{"Haitz's Law"} remains a popular visualization related to the progress in light-emitting diode design and manufacturing, care must be taken to consider its limitations.

@@

@@

consumer experience important
metrics relevant to consumer experience
some are contested
consumer experience metrics have been trated in my thesis \cite{weinold2020technology}.
flicker is out of scope and has been treated in a separate publication
Flicker \cite{weinold2020long}

\begin{figure} [ht]
    \begin{center}
        \includegraphics[width=\textwidth]{SPIE/article/cct_spectrum.pdf}
    \end{center}
    \caption{Color temperature for temperature values between 1,000K and 12,000K. Vertical lines indicate the color temperature of blue light emitting diodes used in combinations with phosphors. Two data points are shown: The 1997 \textit{Nichia} \ch{YAG:Ce^{3+}} (YAG) phosphor at 5800K and the 2004 \textit{Lumileds} \ch{Sr_2Si_5N_8:Eu^{2+}} ("258") phosphor at below 4000K. Color data generated using the \textit{luxpy} package for \textit{Python}. CCT for phosphors computed using the \textit{color science} package for \textit{Python}, from spectral data in publications  \cite{bando1998development,MuellerMach2005}.}
    \label{fig:cct}
\end{figure}

\clearpage
\section{METHODS}
\label{sec:methods}

@@

    \begin{align}
        C_i(\vec{r}) &= C_i^0 \prod_w g_{iw}(r_w) \\
        \Delta C_x &= \int_{t=t_0}^{t_1} C(t) \frac{ \partial \ln C }{ \partial x } \frac{ \text{d} x }{ \text{d} t} \text{d} t \\
        \Delta C_z (t_1,t_2) &\approx \sum_i \tilde{C_i} \ln \frac{g_{iz}(t_2)}{g_{iz}(t_1)}
    \end{align}

    where

@@

\begin{figure} [ht]
    \begin{center}
        \includegraphics[width=\textwidth]{SPIE/article/chip_architectures.pdf}
    \end{center}
    \caption{Cutaway side views of the evolution of chip architectures for classical chip designs (lateral current spreading). Note that dimensions are not to scale and smaller features are greatly exaggerated for visibility. Years correspond to earliest identified patent priority date. Dashed boxes indicate chip designs not brought to large scale production. Adapted from patents \cite{nagahama2013nitride,tanaka2010semiconductor,wierer2006photonic}}
    \label{fig:chip_arch}
\end{figure}

\begin{figure} [ht]
    \begin{center}
        \includegraphics[width=0.85\textwidth]{SPIE/article/droop_lumileds.pdf}
    \end{center}
    \caption{Luminous intensity of four different \textit{Lumileds} high-power light-emitting diodes normalized to the value at a test current of $A_{test}=350$mA. The black curves describe the real measured intensity, the orange curves describe the estimated ideal intensity. Droop is the difference between these curves at the test current. Current-Intensity data extracted from device datasheets \cite{datasheet_lumileds_lux1,datasheet_lumileds_rebel,datasheet_lumileds_rebplus,lumi2019data}}
    \label{fig:chip_arch}
\end{figure}
